---
title: "Round `r params$round`"
output:
  html_document:
    self_contained: false
    toc: true
    toc_depth: 5
date: "Report created `r Sys.Date()`"
params:
  round: 3
---

```{r setup, include = FALSE}
# Settings
knitr::opts_chunk$set(eval = TRUE, echo = FALSE, 
                      message = FALSE, warning = FALSE)
knitr::knit_hooks$set(fig.width = knitr::hook_pngquant)
```

```{r prep}
# Packages
library(knitr)
source("code/load/scenarios.R")
round_text <- paste0("round-", params$round)
```

# Scenarios

```{r describe-scenario, results = 'asis'}
cat(scenarios[[round_text]][["table"]])
```

See also the [full scenario details](`r paste0("https://github.com/covid19-forecast-hub-europe/covid19-scenario-hub-europe/wiki/Round-", params$round)`) for more detail on the common set of assumptions teams used to create their models.

In Round `r params$round`, we asked modellers to start their projections from the `r scenarios[[round_text]][["origin_date"]]`. Data after this date were not included, and as a result, model projections are unlikely to fully account for later information on the changing variants or behavioural patterns.

